Kinematics of the Palomar 5 stellar stream from RR Lyrae stars

### 2019-10-01 paper/main.tex
Updates from Overleaf

Interestingly, there seems to be a strong segregation of the RRL types: all but two of the \NRRab\ \rrab~are found in the cluster tails and two thirds of the \NRRc\ \rrc~are found in the cluster itself. At fixed metallicity and helium abundance, position along the horizontal branch is determined by (present-day) mass, with less massive stars ending up at lower temperatures as type \typeab~stars.
The dichotomy of RRL types between the stream and cluster is therefore suggestive of being a signature of mass segregation: The (slightly) higher mass \rrc\ stars seem to be preferentially more bound to the cluster.
However, the mass difference between \rrab\ and \rrc\ stars is expected to be small, $\lesssim 0.1~\msun$, and so unlikely to have a significantly different dynamical history---this remains an intriguing puzzle.

>>>>

Interestingly, there seems to be a strong segregation of the RRL types: all but two of the \NRRab\ \rrab~are found in the cluster tails and two thirds of the \NRRc\ \rrc~are found in the cluster itself. \changes{
This could be a stochastic effect given the relatively small number of stars, but it seems unlikely given the observed ratios of ab-to-c stars in globular clusters: At the very least, \rrab~stars should account for about half the number of \rrc's \citep[only 5 out of >150 globulars have more than twice as many type~\typec\ than type \typeab\  RRLs, see][]{Clement:2017,Clement:2001,Catelan:2009}. Given the remarkably high completeness of our catalogue, any additional RRL stars would have been detected. Another possibility is that this segregation has a dynamical origin: At fixed metallicity and helium abundance, position along the horizontal branch is determined by (present-day) mass, with less massive stars ending up at higher temperatures as type \typec~stars.
However, if the RRL type segregation had a dynamical origin, the relevant mass should be the one the stars had prior to being ejected from the cluster.} In either case, any of these possible mass differences (either at the main-sequence or the zero-age horizontal branch) are expected to be very small ($\lesssim 0.1~\msun$) and so unlikely to have a significantly different dynamical history---this remains an intriguing puzzle.
